Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

@Carina TODO:
\begin{itemize}
	\item requirements: \\ 
	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
	add unconstraint object co-occurrences / unbiased as far as possible; \\
	rename R1? (lexical alternatives? candidate names?)
	\item title?
\end{itemize}

@@

So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
 State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet (REF!!), though see work by Deng et al. on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
 concepts, adopting the traditional view that there is a single preferred name for a given object.
 Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.

@@

In this Section we discuss requirements for scaling experimental studies on object names as in \cite{graf2016animal} to real-world images.
The difference between these two approaches is illustrated in Figure \ref{fig:graf_genome}, showing  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context.
Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, but we aim for studying object naming as prompted by real-world images. Therefore, we not only need access to names naturally generated by speakers, but also, we need to be able to quantify those factors whose interaction with naming we want to analyze.

Given a natural scene with multiple objects and a target object that a speaker referred to, we need to be able to answer the following questions:

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: \\
        Which name did the speaker use to refer to the target object?
		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
		%Which names are available for the target objects?  
		Which names are available for the target objects? 
		And how are they taxonomically related? 
		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.). 
		%Additionally, in
		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
		Thus, ideally, %names 
		lexical candidates 
		would be grouped according to their taxonomic relations. 
		\item[(3)] \textbf{Contextual informativeness}: \\
		Which names are available for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
\end{itemize}

\cs{Should the following be here or at the beginning of Sect. 4?}
\cs{We could also call below requirements "Desiderata"}
In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.

With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors. 
Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors. 
We summarize this requirement by the term \textbf{R3: unconstraint}. 
Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.

\section{Resources: What Do We Have?}
\label{sec:resources}
%\input{resources}

\paragraph{ImageNet and ILSVRC}

@@

\begin{itemize}
        \item[(R1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
\end{itemize}

\paragraph{Flickr30k Entities}~\\
The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations. 
Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).

\section{Proposal}
%\label{sec:future_proposal}
%\textbf{TODO@Sina (?)}\\
%\input{proposal}

>>>>

%@Carina TODO:
%\begin{itemize}
%	\item requirements: \\ 
%	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
%	add unconstraint object co-occurrences / unbiased as far as possible; \\
%	rename R1? (lexical alternatives? candidate names?)
%	\item title?
%\end{itemize}

@@

So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
 State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet (REF!!), though see work by Deng et al. on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
 concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independentl of the visual context.
 %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.

@@

In this Section we discuss the requirements for  being able to study the context dependence of object names to real-world images, inspired by \cite{graf2016animal}'s study.
 Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus. 
Given a real-world scene with multiple objects and a target object that has to be named, we need access to:

\begin{itemize}

		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
		\item[(3)] the \textbf{natural name} chosen by a speaker for describing or referring to an object

\end{itemize}

For instance, if we want to check whether a specific object like convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible,limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or  a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible,car, etc}.

%\cs{Should the following be here or at the beginning of Sect. 4?}
%\cs{We could also call below requirements "Desiderata"}
%In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
%A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
%Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
%Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation. 
%For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once. 
%
%With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors. 
%Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors. 
%We summarize this requirement by the term \textbf{R3: unconstraint}. 
%Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
%

\section{Resources: What Do We Have?}
\label{sec:resources}

\subsection{ImageNet and ILSVRC}

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases that follows a consistent taxonomy: its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset), such that no (or very few) distractors objects.

@@

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
		\item[(2)] \textbf{Exhaustive annotations}: are not available, as not all objects were annotated with REs and corresponding categories
		   \item[(3)] \textbf{Natural names}: are available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming

\end{itemize}

\subsection{Flickr30k Entities}
The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations. 
Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).

\paragraph{Shortcomings}

By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
		\item[(2)] \textbf{Exhaustive annotations}: are not available
		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

\end{itemize}

%\section{Carina}
%input{resources}

\subsection{Visual Genome}

\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

\paragraph{Shortcomings}

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

\end{itemize}

\section{Possible Solutions}

We now discuss solutions to the shortcomings discussed above.

\subsection{Object detectors}
As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.

\subsection{Post-annotating Captions}
Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation. 
%
In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
such that natural language phrases first needed to be aligned with the image regions they refer to. 
This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study. 
% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)

\subsection{Collect naming data with controlled specificity}

%\label{sec:future_proposal}
%\textbf{TODO@Sina (?)}\\
%\input{proposal}
